Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2021-07-04 papers/paper/paper.tex
Updated exp unbinding plot
Made new figures for paper, added wording and content

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
\davidsays{FIXME remove spring on binding domain and fix caption.}
 \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free. Angles are measured from the $+\hat{x}$ direction. \textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail. Lengths and radii not to scale.}
\label{fig:model}
\end{figure}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{figures/equilibrium.pdf}
\caption{\textbf{Equilibrium configuration.} Model with stiff springs in equilibrium configurations.
}
\label{fig:OBequil}
\end{figure}

@@

\subsection*{$L_t$, $L_s$, $R_b$, $R_m$, $R_s$, $\Theta_{b}$, $\Theta_{m}^{pre}$, $\Theta_{b}^{post}$, $\Theta_{t}$}
Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\theta_{m}^{pre}$, $\theta_{b}^{post}$, $\theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}. In the class average image from Burgess \textit{et. al.} \cite{burgess} the different tail-motor-MTBD angles were taken to indicate that left stalk's motor domain was in the apo post-powerstroke state, and the right stalk's motor domain in the ADP-bound pre-powerstroke state. In the Grotjahn \textit{et. al} \cite{grotjahn} density map, both motor domains were taken to be in the post-powerstroke state.

\subsection*{$C$}
The exponential unbinding parameter $C$ was estimated using the likelihood of leading/lagging head unbinding vs interhead separation data provided in DeWitt \textit{et. al.} \cite{dewitt}. The value of $c$ was chosen which led to the lowest root-mean-squared error in P(lagging step) vs interhead separation between the experiment and the model, as shown in Figure \ref{fig:ProbLagPlot}. All other parameters were held at the values in Table \ref{table:params}.

\begin{figure}[tbhp]
	\centering
	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
	\caption[Lagging preferred steps]{\textbf{Lagging preferred steps.} Likelihood of a trailing step vs. the initial binding domain distance ($P_{trail.}(L)$. Exponential unbinding parameter, $C$, fitted with \cite{Dewitt2012}.}
	\label{fig:ProbLagPlot}
\end{figure}

\subsection*{$k_{ub}$}
The unbinding rate $k_{ub}$ was estimated from stepping trace data in the Yildiz \textit{et. al.} experiment. The $k_{ub}$ value which led to an average velocity of 26 nm/s was chosen, as shown in Figure \ref{fig:TrajPlot}.

@@

\subsection*{$k_b$, $k_{a}$}
The binding and affinity rates directly influenced the onebond stepping statistics shown in Figure \ref{fig:SteppingPlots}. The binding rate controlled the tendency for immediate steps. The affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps. This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein prefered steps within 8 nm.

\subsection*{$c_b$, $c_m$, $c_t$}
Spring constants $c_b$, $c_m$ and $c_t$ were fit using the dynein step length distribution from \cite{yildizpaper}. Three spring constants were drawn uniformly from range $[0.0, 4.0]$ and a simulation was run for 10s simulation time with $k_b=X$, $k_{ub}=Y$, $k_{stk}=Z$, and other parameters noted in Table \ref{tab:params}. One thousand simulations total were run, and the set of spring constants which yielded the lowest root-mean-squared histogram error between the simulation and experimental step length distributions was chosen. \textbf{Probably need to rerun this using our final $k_b$, $k_{ub}$ and $k_{stk}$.}

>>>>

\begin{figure}[tbhp]
\centering
%\includegraphics[width=0.8\linewidth]{figures/bothbound-cartoon-simple-new.pdf}
%\includegraphics[width=0.8\linewidth]{figures/onebound-cartoon-simple-new.pdf}
\includegraphics[width=1\linewidth]{figures/equilibrium-positions-final.pdf}
\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
\davidsays{FIXME remove spring on binding domain and fix caption.}
 \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free. Angles are measured from the $+\hat{x}$ direction. \textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail. Lengths and radii not to scale.}
\label{fig:model}
\end{figure}

@@

@@

The model's simplistic nature allowed flexible optimization for each parameter in order to most accurately portray stepping results from experiment. We investigated this parameter space by associating each stepping parameter to a property of dynein's step observed from Yildiz's experiment. Dynein most properly demonstrated forward motility and correlated stepping when binding rates increased to promote $<$8 nm step sizes and $<$100 ns unbound times. The 2-HB state dominated dynein's dwell time, while the 1-HB state happened almost instantaneous, forcing the velocity to be highly dependent on the unbding parameters. Consequently, dynein fails to equilibrate during the stepping motion and quickly rebinds shortly after unbinding.

We first estimated structural parameters $L_t$, $L_s$, $R_b$, $R_m$, $R_s$, and equilibrium angles $\theta_{m}^{pre}$, $\theta_{m}^{post}$, and $\theta_{t}$ from cryo-electron microscopy class averages and density maps of cytoplasmic and axonoemal dynein, shown in Figure \ref{fig:micrographs}. We defined the tail and motor equilibrium angles from Burgess \textit{et al. } class average image, where the left stalk's motor was in the apo post-powerstroke state and right stalk's motor was in the ADP-bound apo pre-powerstroke state.

%Structural parameters $L_t$, $L_s$, $R_b$, $R_m$, and $R_s$ and equilibrium angles $\theta_{m}^{pre}$, $\theta_{b}^{post}$, $\theta_{t}$ were estimated using cryo-electron microscopy class averages and density maps of cytoplasmic and axonemal dynein, shown in Figure \ref{fig:micrographs}. In the class average image from Burgess \textit{et. al.} \cite{burgess} the different tail-motor-MTBD angles were taken to indicate that left stalk's motor domain was in the apo post-powerstroke state, and the right stalk's motor domain in the ADP-bound pre-powerstroke state. In the Grotjahn \textit{et. al} \cite{grotjahn} density map, both motor domains were taken to be in the post-powerstroke state.

%
%\subsection*{$C$}
We determined the exponential unbinding parameter $C$ based on the likelihood for a lagging head to unbind vs. the interhead separation provided from DeWitt \textit{et. al.} \cite{dewitt}. A test for the lowest root-mean-squared error between the experiment and the model generated a value of $C=-0.35$, as shown in Figure \ref{fig:ProbLagPlot}. This parameter governs the tension-gating between dynein's heads, as the probability of a lagging step increases with $C$. All other parameters were held at the values in Table \ref{table:params}.

\begin{figure}[tbhp]
	\centering
	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.35}
	\caption[Lagging preferred steps]{\textbf{Lagging preferred steps.} Likelihood of a trailing step vs. the initial binding domain distance ($P_{trail.}(L)$. Exponential unbinding parameter, $C$, fitted with \cite{Dewitt2012}.}
	\label{fig:ProbLagPlot}
\end{figure}

%\subsection*{$k_b$, $k_{a}$}
The binding and affinity rates directly influenced the stepping statistics shown in Figure \ref{fig:SteppingPlots}. The binding rate controlled the tendency for immediate steps, while the affinity rate controlled the transition time from low affinity to high affinity and introduced a buffer time after unbinding to prevent instantaneous steps. This was crucial when fitting to Yildiz's slope of m = -0.4, as our model was only able to replicate the stepping correlation if dynein stepped within 8 nm 56\% of the time.

%\subsection*{$k_{ub}$}
Due to dynein's step equilibrating during the 2-HB state, the time spent reaching this equilibrium heavily influences the velocity of a walk. Similarly, the ATP concentration controls the rate of steps and the time spent in the 2-HB state. Thus, we matched the unbinding rate $k_{ub}$ from stepping trace data in the Yildiz \textit{et. al.} experiment which led to an average velocity of 26 nm/s. The unbinding rate directly correlates to the rate of steps, as the inverse, $k_{ub}^{-1}$, is the average time spent in the 2-HB state. This fitting is shown in Figure \ref{fig:TrajPlot}.

@@

%
%\subsection*{$c_m$, $c_t$}
The motor and tail spring constants, $c_m$ and $c_t$, relates to the tendency for equilibrium positions in the 1-HB and 2-HB state. We picked these parameters in accordance to the model's ability to perform the powerstroke and achieve processive motion. With these spring constants, the model dynein preferred forward steps towards the minus-end rather than backward steps, while still maintaining flexibility within the stalk and stapping variance.
